Data Analysis Methods for the Detection of the Epoch of Reionization

### 2017-11-29 PAPER.tex
minor edits

\begin{figure*}
	\centering
	\includegraphics[trim={0.3cm 0.2cm 1cm 0.3cm},clip,height=0.3\textwidth]{plots/toy_sigloss3.png}
	\includegraphics[trim={1cm 0.2cm 0cm 0.3cm},clip,height=0.3\textwidth]{plots/toy_sigloss4.png}
	\caption{Resulting power spectrum estimates for the toy model simulation described in Section \ref{sec:toymodel} --- 
foregrounds only (blue), EoR only (red), and the weighted FG + EoR dataset (green). We use inverse covariance weighting 
where $\textbf{C}$ is derived from the data (left), contrasted with projecting out the first eigenmode only (right). In the former 
case, signal loss arises from using information from all eigenmodes of $\hat{\textbf{C}}$. Because $\hat{\textbf{C}}$ is 
empirically estimated, its eigenvalues pose the risk of describing random fluctuations that happen to exist in the data realization 
but may not exist in the true covariance. Consequently, these modes are over-fitted and down-weighted, leading to signal loss. 
There is no signal loss when using only the zeroth eigenmode, since we are not using information from the weaker eigenmodes 
which $\hat{\textbf{C}}$ does not describe accurately.}
	\label{fig:toy_sigloss3}
\end{figure*}

>>>>

\begin{figure*}
	\centering
	\includegraphics[trim={0.3cm 0.2cm 1cm 0.3cm},clip,height=0.3\textwidth]{plots/toy_sigloss3.png}
	\includegraphics[trim={1cm 0.2cm 0cm 0.3cm},clip,height=0.3\textwidth]{plots/toy_sigloss4.png}
	\caption{Resulting power spectrum estimates for the toy model simulation described in Section \ref{sec:toymodel} --- 
foregrounds only (blue), EoR only (red), and the weighted FG + EoR dataset (green). The foregrounds peak at a $k$ mode based on the frequency of the sinusoid used to create it. We compare inverse covariance weighting 
where $\textbf{C}$ is derived from the data (left), with projecting out the first eigenmode only (right). In the former 
case, signal loss arises from using information from all eigenmodes of $\hat{\textbf{C}}$. Because $\hat{\textbf{C}}$ is 
empirically estimated, its eigenvalues pose the risk of describing random fluctuations that happen to exist in the data realization 
but may not exist in the true covariance. Consequently, these modes are over-fitted and down-weighted, leading to signal loss. 
There is no signal loss when using only the zeroth eigenmode, since we are not using information from the weaker eigenmodes 
which $\hat{\textbf{C}}$ does not describe accurately.}
	\label{fig:toy_sigloss3}
\end{figure*}
